\documentclass{supervision}
\usepackage{course}

\Supervision{2}
\Topics{Graphics pipeline, algorithms for 2D and 3D}

\begin{document}

\section*{Warmup Questions}
\begin{questions}
    \question
    Give as many reasons as possible why we use matrices to represent transformations. Explain why we use homogeneous coordinates.
    \question
    Are there any problems with texture mapping onto a sphere?
    \question
    Describe how Phong's specular reflection models real specular reflection. Whyis it only a rough approximation? Why is it useful?
    \question
    Draw pictures to show what is meant by:
    \begin{parts}
        \part{object coordinates}
        \part{world coordinates}
        \part{viewing coordinates}
        \part{screen coordinates}
    \end{parts}
    \question
    We use a lot of triangles to approximate stuff in computer graphics. Why are they good? Why are they bad? Can you think of any alternatives?

\end{questions}

\section*{Longer Questions}
\begin{questions}
    \SetQuestionNumber{3}
    \question
    Draw and explain two different scenes which have the same projection asseen by the viewer. What other cues can you give so that the viewer can distinguish the depth information?
    \SetQuestionNumber{6}
    \question
    We often use triangles to represent a sphere. Describe twomethods of generating triangles from a sphere.
    \question
    Compare and contrast:
    \begin{itemize}
        \item{texture mapping}
        \item{bump mapping}
        \item{displacement mapping}
    \end{itemize}
    \SetQuestionNumber{10}
    \question
    \begin{parts}
        \part{Show how to perform 2D rotation around an arbitrary point.}
        \part{Show how to perform 3D rotation around an arbitrary axis parallel to the x-axis.}
        \part{Show how to perform 3D rotation around an arbitrary axis.}
    \end{parts}
    
\end{questions}

\section*{Advanced Questions}
\begin{questions}
    \SetQuestionNumber{3}
    \question
    Define and then compare and contrast the following methods of specifying rotation in 3D.
    
    \textit{You will need to look these up}.
    \begin{parts}
        \part{Quarternions}
        \part{Euler Angles}
    \end{parts}
    \question
    Find out about the Coo-Torrance shading model and explain how this improves on the naïve diffuse+specular+ambient model.

\end{questions}

\section*{Practical Programming}
\begin{questions}
    \question
    Write a program using OpenGL to display the scene that you rendered with your ray-tracer. Explore some different surface models in the fragment shader.
\end{questions}


\end{document}
